Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-06-28 manuscript/draftcssa19.tex
Break out analysis section to separate file.

While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-Renyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks. We also address more empirically grounded models in the concluding section of this paper.

@@

\section{Analysis}

>>>>

While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks. We also address more empirically grounded models in the concluding section of this paper.

@@

\section{Analysis}
\include{analysis}
